Homelessness and Drug Toxicity

### 2024-03-16 paper/paper.qmd
update model section

I DO NOTKNOW WHAT TO PUT HERE Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

>>>>

We have completed a number of tests on our model which can be viewed in the @sec-model-details. These are vital to ensure our model achieves what is outlined in the paper.
